Non-Vertical Cultural Transmission and the\\ Evolution of Cooperation

### 2020-09-01 ms/main.tex
Revisit figure 5 caption - add the values of the parameters and update the name of the figures files
Switch between figure 3a and figure 3b so we start with alpha = 0 and then move to alpha > 0
Fix figure 3 references

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Discussion
\section*{Discussion}
We hypothesized that non-vertical transmission can explain the evolution of cooperation and evaluated this hypothesis using a deterministic discrete-time evolutionary model with fitnesses in the form of payoffs from a prisoner's dilemma game.
Under oblique and horizontal transmission, horizontal transmission bias for the cooperative phenotype was found to be sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).
Under horizontal and vertical cultural transmission, cooperation, or defection can fix, or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the correlation between cooperation and transmission (Result~\autoref{result:vert_hori}).
Under a combination of vertical, oblique, and horizontal transmission the dynamics are much more complicated. However, we show that under some conditions cooperation can evolve, and can even be maintained in stable coexistence with defection (Result~\autoref{result:vert_obli_hori}).
We saw that it is likely to find configuration of parameters that results coexistence as can be seen in \autoref{fig:results2}a. In figure \autoref{fig:results2}a the yellow area in which coexistence occur has horizontal bias that favor defection ($T_B>T_A$) and the cost is relatively small.

@@

\citet{woodcock2006significance} showed the importance of non-vertical transmission for the evolution of cooperation. In their model the individuals interact according to standard prisoner dilemma game.
However, they do not link between interaction and transmission. In terms of our model they have chosen the assortative meeting coefficient $\alpha$ to be zero. Our results are more general since it shows the importance of assortative meeting for the evolution of cooperation.

@@

\begin{figure}[htb]
  \centering
  % TODO for some reason figs a and b have a lot of white space on their right side
    \includegraphics[scale=0.75]{boundiries_non_zero_alpha.pdf}

@@

    \includegraphics[scale=0.75]{boundiries_withAlpha_y_axis.pdf}
    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
(\textbf{a-b})~the cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines. 
(\textbf{c})~the assortment $\alpha$ is on the y-axis; the assortment boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0.7$.(\textbf{b})~$\alpha = 0$. (\textbf{c})~$c = 0.35$.
  % TODO missing text descriptions of conditions on (3)
  	}
    \label{fig:results2}
\end{figure}

@@

%%% Figure: frequency dynamics
\begin{figure}[htb]
  \centering
    \includegraphics[scale=0.7]{figure3a.pdf}
    \includegraphics[scale=0.7]{figure3b.pdf}
    \includegraphics[scale=0.7]{figure3c.pdf}
  \caption{
  \textbf{Dynamics of the frequency of cooperation.}
  The frequency $\tilde{p}$ of parents with cooperative phenotype $A$ in \textbf{(a-b)} and the frequency $p$ of adults with cooperative phenotype $A$ in \textbf{(c)}.
  The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable coexistence of cooperators and defectors (yellow).
  (a) $v=1$, $T_A=T_B=T$, $\alpha \neq 0$; (b) $v=1$, $\alpha = 0$; (c) $v=0$.
  % TODO write all parameter values. T=? alpha=?
  % TODO set colors the same as fig 3.
  % TODO remove legends, increase fonts, explain in caption instead of legend.
  }
  \label{fig:results}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Discussion
\section*{Discussion}
We hypothesized that non-vertical transmission can explain the evolution of cooperation and evaluated this hypothesis using a deterministic discrete-time evolutionary model with fitnesses in the form of payoffs from a prisoner's dilemma game.
Under oblique and horizontal transmission, horizontal transmission bias for the cooperative phenotype was found to be sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).
Under horizontal and vertical cultural transmission, cooperation, or defection can fix, or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the correlation between cooperation and transmission (Result~\autoref{result:vert_hori}).
Under a combination of vertical, oblique, and horizontal transmission the dynamics are much more complicated. However, we show that under some conditions cooperation can evolve, and can even be maintained in stable coexistence with defection (Result~\autoref{result:vert_obli_hori}).
We saw that it is likely to find configuration of parameters that results coexistence as can be seen in \autoref{fig:results2}b. In figure \autoref{fig:results2}b the yellow area in which coexistence occur has horizontal bias that favor defection ($T_B>T_A$) and the cost is relatively small.

@@

@@

\begin{figure}[htb]
  \centering
  % TODO for some reason figs a and b have a lot of white space on their right side

@@

    \includegraphics[scale=0.75]{boundiries_non_zero_alpha.pdf}

    \includegraphics[scale=0.75]{boundiries_withAlpha_y_axis.pdf}
    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
(\textbf{a-b})~the cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines. 
(\textbf{c})~the assortment $\alpha$ is on the y-axis; the assortment boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
  % TODO missing text descriptions of conditions on (3)
  	}
    \label{fig:results2}
\end{figure}

@@

%%% Figure: frequency dynamics
\begin{figure}[htb]
  \centering
    \includegraphics[scale=0.7]{Time_Figure_Equal_Horizontal.pdf}
    \includegraphics[scale=0.7]{Time_Figure_Only_Vertical_No_Alpha.pdf}
    \includegraphics[scale=0.7]{Time_Figure_No_Vertical.pdf}
  \caption{
  \textbf{Dynamics of the frequency of cooperation.}
  The frequency $\tilde{p}$ of parents with cooperative phenotype $A$ in \textbf{(a-b)} and the frequency $p$ of adults with cooperative phenotype $A$ in \textbf{(c)}.
  The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable coexistence of cooperators and defectors (yellow).
  \textbf{(a)} $v=1$, $T_A=T_B=T = 0.2$, $\alpha = 0.5 \neq 0$, $\tilde{p}_0 = 0.5$ and $c=0.1$; \textbf{(b)} $v=1$, $\alpha = 0$, $\tilde{p}^* \approx 0.35$, $T_A = 0.65$, $T_B = 0.1$, $b=1.3$ and $c=0.65$; \textbf{(c)} $v=0$, $\alpha =0.5$, $p_0 = 0.5$, $T_A = 0.5$, $b=1.3$ and $c = 0.5$.
  % TODO write all parameter values. T=? alpha=?
  % TODO set colors the same as fig 3.
  % TODO remove legends, increase fonts, explain in caption instead of legend.
  }
  \label{fig:results}
\end{figure}
